---
name: Neves
surname: Ana
profilepic: "./Images/profile.jpeg"
position: "Psychology PhD Researcher"
address: "University of Sussex, Brighton, UK"
# phone: +1 22 3333 4444
email: "A.Neves@sussex.ac.uk"
# twitter: Dom_Makowski
github: AnafNeves
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
    \RaggedRight  Doctoral Tutor and PhD researcher in Psychology at the University of Sussex, supervised by Dr Dominique Makowski. My research explores the role of interoception - our perception of internal bodily states - in shaping emotional experiences and beliefs about reality. I use a combination of behavioural tasks and physiological measures to investigate how bodily awareness influences responses to emotionally evocative stimuli.
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "8e7cc3"
output:
    vitae::awesomecv:
        page_total: true
        keep_md: true
editor_options:
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

<!-- # Current Position -->

<!-- ```{r CurrentEmployment} -->
<!-- data <- tibble( -->
<!--   what = "Lecturer in Psychology", -->
<!--   when = "2023 - Present", -->
<!--   with = "University of Sussex", -->
<!--   where = "UK", -->
<!--   details = c( -->
<!--     paste( -->
<!--       "Full teaching service on courses such as Quantitative and Qualitative Methods." -->
<!--     ), -->
<!--     paste( -->
<!--       "Head of the ", -->
<!--        link("Reality Bending Lab", "https://realitybending.github.io/"), -->
<!--       " (ReBeL) where we study reality perception (e.g., neuroscience of deception, perception of fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, open source software and neurophysiological techniques)." -->
<!--     ) -->
<!--   ) -->
<!-- ) -->

<!-- vitae::detailed_entries(data, with, when, what, where, details, .protect = FALSE) -->
<!-- ``` -->

<!-- \footnotesize -->

<!-- The NTU "presidential postdoc fellowship" is a competitive grant meant as an intermediate step between postdoc and faculty. While integrated within a larger lab (the [Clinical Brain Lab](https://www.clinicalbrain.org/), directed by Prof Annabel Chen), I am pursuing my own research track on the perception of reality, managing my team (3 research assistants, and several undergrad students) and research funding ($ 200k). I am involved in all the research and administrative aspects of the project (writing IRBs, project budgeting, experiment creations, data collection, analysis, manuscript writing, ...). -->

<!-- On top of the mentoring and teaching done in the context of the lab, I am also involved in university lectures (e.g., statistics for NTU students), research-oriented workshops (for instance, I have introduced our software *NeuroKit* at the OHBM conference this summer), and other courses (I have been recently appointed by the University of Zurich to give a 3 days course on Python to their PhD students). -->

\normalsize

# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2024 - ",
  with = "University of Sussex",
  where = "UK",
  details = paste0(
    "supervised by ",
    link("Dr. Dominique Makowski", "https://dominiquemakowski.github.io/")
  )
), tibble(
  what = "Research Masters (MRes) in Psychological Methods",
  when = "2023 - 2024",
  with = "Univeristy of Sussex",
  where = "UK",
  details = NA
), tibble(
  what = "Bachelor of Science (BSc) - Psychology with Cognitive Science",
  when = "2018 - 2022",
  with = "University of Sussex",
  where = "UK",
  details = NA
))

if (short) {
  data <- data[1:3, ]
  data$details <- NA
}

vitae::detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```

# Experience

## Teaching

```{r ExperienceTeaching}
data <- rbind(
  tibble(
  Position = "Doctoral Tutor for Quantitative and Qualitative Methods",
  Date = "Jan-Apr, 2025",
  Institution = "University of Sussex",
  Where = "Brighton, UK",
  Activity = paste0("Facilitated students’ critical engagement with quantitative and qualitative research methods in psychology, with a particular focus on measurement issues and the interpretive decisions researchers make when investigating complex psychological constructs.")
), tibble(
  Position = "Doctoral Tutor for Discovering Statistics",
  Date = "Sep-Dec, 2024",
  Institution = "University of Sussex",
  Where = "Brighton, UK",
  Activity = paste0("Supported students in developing both theoretical understanding and practical skills in implementing, interpreting, and reporting statistical analyses, with a focus on the linear model.")
))

# Save for re-useability
write.csv(data, "data/experience_teaching.csv", row.names = FALSE, fileEncoding = "UTF-8")

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

# Skills

## Language

\small

-   **Portuguese**: Native
-   **English**: Fluent

\normalsize

## Research

\small

My PhD investigates how awareness that a stimulus is ‘fake’ influences emotional and belief-related responses, and seeks to identify the factors that shape these reality judgments. A key focus is the role of interoception in modulating affective responses - measured in terms of intensity, valence, and eroticism. We are also keen on exploring the use of transcutaneous vagus nerve stimulation (tVNS) to manipulate interoceptive sensitivity, with the aim of determining whether such modulation affects both physiological and subjective responses to stimuli labelled as ‘fake’, as well as their perceived realism.

\normalsize

\small

## Techniques, Methods and Open Science

I am currently developing technical expertise in EEG, physiological signal processing, and computational methods including Bayesian modelling. Aligned with my supervisor’s (`r link("\\textbf{GitHub}", "https://github.com/DominiqueMakowski")`) commitment to open science, I actively contribute to open-source communities (e.g., on `r link("\\textbf{GitHub}", "https://github.com/AnafNeves")`) to support accessibility and transparency in research.

I am committed to the highest standards of open and reproducible science, routinely sharing data, materials, and analysis scripts. This commitment is grounded in a strong emphasis on methodological rigour and ethical responsibility throughout the research process.

## Other Projects

I am also currently collaborating on a project outside my PhD with a PhD researcher at Macquarie University in Sydney, Australia (`r link("\\textbf{GitHub}","https://github.com/Tam-Pham")`). The project is a meta-analysis examining the association between psychopathology and heart rate variability.

# Publications

Makowski, D., Te, A. S., **Neves, A.**, Kirk, S., Liang, N. Z., Mavros, P., & Chen, S. A. (2025). [Too beautiful to be fake: Attractive faces are less likely to be judged as artificially generated](https://doi.org/10.1016/j.actpsy.2024.104670). _Acta Psychologica_, 252, 104670.

Makowski, D., Te, A. S., **Neves, A.**, & Chen, S. A. (2025). [Measuring Depression and Anxiety With 4 Items? Adaptation of the PHQ-4 to Increase Its Sensitivity to Subclinical Variability Open Access](https://doi.org/10.1525/collabra.143431). _Collabra: Psychology_, 11(1), 143431.

## Pre-Prints

\small

Makowski, D., **Neves, A.**(2025). [Testing the Relationship between Phenomenological Control related to Illusion Sensitivity](https://doi.org/10.31234/osf.io/873th_v3)

Makowski, D., **Neves, A.**, & Field, A. (2025). [Introducing the Choice-Confidence (CHOCO) Model for Bimodal Data from Subjective Ratings: Application to the Effect of Attractiveness on Reality Beliefs about AI-Generated Faces](https://osf.io/preprints/psyarxiv/z68v3_v1)

Makowski, D., **Neves, A.**, Benn, E. L., Bennett, M., & Poerio, G. (2025). [The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS](https://osf.io/preprints/psyarxiv/8qrht_v1)

\normalsize

# References

\small

Contact in case of inquiry.

-   **Dr Dominique Makowski** (PhD supervisor): d.makowski@sussex.ac.uk

\normalsize
